R Notebook

### 2016-09-26 mixed-model.Rmd
play with results

predictions %>% 
  group_by(year) %>% 
  summarize(mean(diff^2)) %>% 
  plot(ylab = "Mean Squared Errorr", type = "l", ylim = c(0, 50))

predictions %>% 
  filter(observer_id %in% train$observer_id) %>% 
  group_by(year) %>% 
  summarize(mean(diff^2)) %>% 
  lines(col = 2)
legend("topleft", 
       legend = c("all observations", "known observers only", "training observations"), 
       lty = c(1, 1, 2), col = c(1, 2, 1))

abline(h = var(resid(model)), lty = 2)
```

@@

>>>>

predictions = predictions %>% 
  mutate(observer_count = c(table(train$observer_id)[as.character(observer_id)])) %>% 
  mutate(observer_count = ifelse(is.na(observer_count), 0, observer_count)) %>% 
  mutate(observer_class = cut(observer_count, c(-Inf,0, 2^(0:7), Inf)))

predictions %>% 
  group_by(year, observer_class) %>% 
  summarize(rmse = sqrt(mean((richness - predicted)^2))) %>% 
  ggplot(aes(x = year, y = rmse, color = observer_class)) + 
  geom_smooth(se = FALSE, span = 2)

#predictions %>% 
#  filter(observer_id %in% train$observer_id) %>% 
#  group_by(year) %>% 
#  summarize(mean(diff^2)) %>% 
#  lines(col = 2)
#legend("topleft", 
#       legend = c("all observations", "known observers only", "training observations"), 
#       lty = c(1, 1, 2), col = c(1, 2, 1))

#abline(h = var(resid(model)), lty = 2)
```

@@

```
```{r}
sapply(1:ncol(autocorr_matrix),
       function(i){
         mean(autocorr_matrix[row(autocorr_matrix) == (col(autocorr_matrix) - i)])
       }
)
```

```{r}
